---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qmdcv

<!-- badges: start -->
[![R-CMD-check](https://github.com/kthayashi/qmdcv/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kthayashi/qmdcv/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

`qmdcv` is an R package that facilitates creation of a curriculum vitae (CV) with [Quarto](https://quarto.org). The core functionality of the package is to convert data that comprise a CV, supplied in [YAML](https://yaml.org) format, into Quarto's flavor of [Markdown](https://quarto.org/docs/authoring/markdown-basics.html) text. This text can be inserted into a Quarto (.qmd) document and rendered to HTML.

## Installation

You can install `qmdcv` from GitHub:

```{r eval=FALSE}
install.packages("pak")
pak::pkg_install("kthayashi/qmdcv")
```

You will also need to [install Quarto](https://quarto.org/docs/get-started) to make use of the functionality of this package. Recent versions of RStudio come bundled with Quarto.

## Usage

```{r}
library(qmdcv)
```

`qmdcv` provides a YAML file containing example CV data:

```{r}
write_example()
```

We can read this YAML file into R as a list:

```{r}
cvdata <- read_example()
```

Or equivalently:

```{r eval=FALSE}
cvdata <- yaml::read_yaml(file = system.file("example.yaml", package = "qmdcv"))
```

where `file` can be replaced with the path to your own CV data.

The family of `insert()` functions converts a list of CV data into Markdown text in a number of pre-defined formats. For example, we can insert education history into a CV with:

```{r}
insert(cvdata$education)
```

⚠️ Set `output: asis` (or `results: asis` for `knitr`) in code chunks to ensure that this Markdown text is treated as such upon render.

You can get started by using `write_example()` to make a copy of the example YAML file as a template for entering your own CV data. See [here](https://github.com/kthayashi/cv) for my personal CV built using `qmdcv`.

## Disclaimers

This package was inspired by the [`datadrivencv`](https://nickstrayer.me/datadrivencv) and [`vitae`](https://pkg.mitchelloharawild.com/vitae) packages and is intended for personal use.

This package is neither associated with nor endorsed by the Quarto open source project.
