---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qmdcv

<!-- badges: start -->
<!-- badges: end -->

This package facilitates creating a curriculum vitae (CV) with
[Quarto](https://quarto.org/). The core functionality of the package is to
convert structured data for a CV, supplied as a YAML file(s) and/or lists in R,
into Markdown text. This text can be inserted into a .qmd file and rendered as
an HTML document with Quarto.

This package was inspired by the
[`vitae`](https://github.com/mitchelloharawild/vitae/) and
[`datadrivencv`](https://github.com/nstrayer/datadrivencv) packages.

## Disclaimers

- This package is neither associated with nor endorsed by the Quarto open source
project.
- I'm building out this package as I go, primarily for my own use. Anyone is
welcome to use this package and open issues/pull requests, but I may not be able
to implement certain changes until they become necessary in my own workflow.

## Installation

You can install the development (and only) version of `qmdcv` from
[GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("kthayashi/qmdcv")
```

## Example

Here's a demonstration of the package using the bundled `example_data`:

```{r}
library(qmdcv)
data(example_data)
```

The family of `insert()` functions takes a list of one or more lists containing
CV data and produces Markdown text in a select few formats. For example,
education data can be provided as:

```{r}
edu <- example_data$education
str(edu)
```

Expected usage is to enter CV data in a YAML file, which can be read into R
using the [`yaml`](https://github.com/vubiostat/r-yaml/) package. Here's what
the education data above would look like in YAML format:

```{r}
cat(yaml::as.yaml(edu))
```

Use `insert()` to produce Markdown text from the data in `edu`:

```{r}
insert(edu)
```

Note: Use the Quarto option `output: asis` to get the produced Markdown text to
be rendered properly.
