---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qmdcv

<!-- badges: start -->
[![R-CMD-check](https://github.com/kthayashi/qmdcv/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kthayashi/qmdcv/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

This package facilitates creating a curriculum vitae (CV) with [Quarto](https://quarto.org/). The core functionality of the package is to convert structured data for a CV, supplied as a YAML file and/or lists in R, into Quarto's flavor of Markdown text. This text can be inserted into a .qmd document and rendered as an HTML document with Quarto.

This package is intended primarily for personal use and was inspired by the [`vitae`](https://github.com/mitchelloharawild/vitae/) and [`datadrivencv`](https://github.com/nstrayer/datadrivencv) packages.

## Installation

Install `qmdcv` from GitHub:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("kthayashi/qmdcv")
```

To make use of the functionality of this package, you will need to install Quarto separately. If you are using a recent version of RStudio, Quarto may already be available to you. In addition, one function in this package (`insert_pubs_web()`) uses the [Font Awesome Extension](https://github.com/quarto-ext/fontawesome) for Quarto - if you would like to use this function, you will need to install this extension to the root directory of your project.

## Usage

Here's a demonstration of `qmdcv` using the bundled `cvdata`:

```{r}
library(qmdcv)
data(cvdata)
```

The family of `insert()` functions takes a list of one or more lists containing CV data and produces Markdown text in a select few formats. For example, education data can be provided as:

```{r}
(edu <- cvdata$education)
```

Expected usage is to enter CV data in a YAML file, which can be read into R using the [`yaml`](https://github.com/vubiostat/r-yaml/) package. Here's what the education data above would look like in YAML format:

```{r}
cat(yaml::as.yaml(edu))
```

Use `insert()` to produce Markdown text from the data in `edu`:

```{r}
insert(edu)
```

**Important**: Use the Quarto option `output: asis` to ensure that the inserted Markdown text can be rendered properly.

See [here](https://github.com/kthayashi/cv) for my personal CV built using `qmdcv`.

## Disclaimers

This package is neither associated with nor endorsed by the Quarto open source project.
